Anony\emph{mice}d shareable data: Using \emph{mice} to create and analyze multiply imputed synthetic data sets

### 2021-10-04 manuscript/Manuscript.tex
update with cached sims

To induce sampling variance, 1000 bootstrap samples of the \texttt{boys}
data will be synthesized with \(m = 5\) imputations. Synthetic values
are generated using the \texttt{CART} imputation method for all columns,
except for \texttt{bmi}. The deterministic relation \texttt{bmi} which
will be synthesized passively based on the synthetic values for
\texttt{hgt} and \texttt{wgt} to preserve the relation in the synthetic
data. Additional parameters that come with the use of
\texttt{mice.impute.cart()} are the complexity parameter \texttt{cp} and
the minimum number of observations in any terminal node
\texttt{minbucket}, that both constrain the flexibility of the
imputation model. The values of the parameters \texttt{cp} and
\texttt{minbucket} ought to adhere to the call for imputation models
that are as flexible as possible. Appropriate values for these
parameters, as well as the input for the \texttt{predictorMatrix},
depend on the data at hand. In the current example, the complexity
parameter is specified at \texttt{cp\ =\ 1e-08} rather than the default
value \texttt{1e-04}, and the minimum number of observations in each
terminal node is set at \texttt{minbucket} \(= 3\) rather than the
default value \(5\). By allowing for more complexity in the imputation
model, bias in the estimates from the synthetic data set is reduced.
Additionally, since the missingness pattern is monotone, the number of
iterations can be set to \texttt{maxit\ =\ 1}.

@@

\[
\bar{u}_m = \sum_{l = 1} \frac{u^{(l)}}{m},
\] with \(u^{(l)}\) reflecting the variance estimate in the \(l\)th
synthetic data set.

@@

>>>>

To induce sampling variance, 1000 bootstrap samples of the \texttt{boys}
data have been synthesized with \(m = 5\) imputations for every data
cell. Synthetic values are generated using the \texttt{CART} imputation
method for all columns, except for \texttt{bmi}. The deterministic
relation \texttt{bmi} which will be synthesized passively based on the
synthetic values for \texttt{hgt} and \texttt{wgt} to preserve the
relation in the synthetic data. Additional parameters that come with the
use of \texttt{mice.impute.cart()} are the complexity parameter
\texttt{cp} and the minimum number of observations in any terminal node
\texttt{minbucket}, that both constrain the flexibility of the
imputation model. The values of the parameters \texttt{cp} and
\texttt{minbucket} ought to adhere to the call for imputation models
that are as flexible as possible. Appropriate values for these
parameters, as well as the input for the \texttt{predictorMatrix},
depend on the data at hand. In the current example, the complexity
parameter is specified at \texttt{cp\ =\ 1e-08} rather than the default
value \texttt{1e-04}, and the minimum number of observations in each
terminal node is set at \texttt{minbucket} \(= 3\) rather than the
default value \(5\). By allowing for more complexity in the imputation
model, bias in the estimates from the synthetic data set is reduced.
Additionally, since the missingness pattern is monotone, the number of
iterations can be set to \texttt{maxit\ =\ 1}.

@@

\[
\bar{u}_m = \sum_{l = 1} \frac{u^{(l)}}{m},
\] where \(u^{(l)}\) denotes the variance estimate in the \(l\)th
synthetic data set.

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plan}\NormalTok{(multisession) }\CommentTok{\# increase speed through futures}

\NormalTok{true\_model\_age }\OtherTok{\textless{}{-}} \FunctionTok{lm}\NormalTok{(age }\SpecialCharTok{\textasciitilde{}}\NormalTok{ wgt }\SpecialCharTok{+}\NormalTok{ hgt, data) }\CommentTok{\# model 1}
\NormalTok{true\_model\_wgt }\OtherTok{\textless{}{-}} \FunctionTok{lm}\NormalTok{(wgt }\SpecialCharTok{\textasciitilde{}}\NormalTok{ age }\SpecialCharTok{+}\NormalTok{ hgt, data) }\CommentTok{\# model 2}
\NormalTok{true\_model\_gen }\OtherTok{\textless{}{-}}\NormalTok{ MASS}\SpecialCharTok{::}\FunctionTok{polr}\NormalTok{(gen }\SpecialCharTok{\textasciitilde{}}\NormalTok{ age }\SpecialCharTok{+}\NormalTok{ hc }\SpecialCharTok{+}\NormalTok{ reg, data, }\AttributeTok{Hess =} \ConstantTok{TRUE}\NormalTok{) }\CommentTok{\# model 3}

\NormalTok{coefs\_age }\OtherTok{\textless{}{-}}\NormalTok{ broom}\SpecialCharTok{::}\FunctionTok{tidy}\NormalTok{(true\_model\_age)}\SpecialCharTok{$}\NormalTok{estimate }\CommentTok{\# extract coefficients of model 1}
\NormalTok{coefs\_wgt }\OtherTok{\textless{}{-}}\NormalTok{ broom}\SpecialCharTok{::}\FunctionTok{tidy}\NormalTok{(true\_model\_wgt)}\SpecialCharTok{$}\NormalTok{estimate }\CommentTok{\# extract coefficients of model 2}
\NormalTok{coefs\_gen }\OtherTok{\textless{}{-}}\NormalTok{ broom}\SpecialCharTok{::}\FunctionTok{tidy}\NormalTok{(true\_model\_gen)}\SpecialCharTok{$}\NormalTok{estimate }\CommentTok{\# extract coefficients of model 3}

\NormalTok{nsim }\OtherTok{\textless{}{-}} \DecValTok{1000} \CommentTok{\# use 1000 iterations}

\NormalTok{bootstrap\_samples }\OtherTok{\textless{}{-}} 
\NormalTok{  modelr}\SpecialCharTok{::}\FunctionTok{bootstrap}\NormalTok{(}\AttributeTok{data =}\NormalTok{ data, }\AttributeTok{n =}\NormalTok{ nsim) }\SpecialCharTok{\%$\%} 
\NormalTok{  strap }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{map}\NormalTok{(as\_tibble)}

\NormalTok{post }\OtherTok{\textless{}{-}} \FunctionTok{make.post}\NormalTok{(data)}
\NormalTok{post[}\StringTok{"bmi"}\NormalTok{] }\OtherTok{\textless{}{-}} \StringTok{"imp[[j]][, i] \textless{}{-} imp[[\textquotesingle{}wgt\textquotesingle{}]][, i] / (imp[[\textquotesingle{}hgt\textquotesingle{}]][, i] / 100)\^{}2"}

\NormalTok{synthetic\_samples }\OtherTok{\textless{}{-}} 
\NormalTok{  bootstrap\_samples }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{future\_map}\NormalTok{(}\ControlFlowTok{function}\NormalTok{(x) \{}
\NormalTok{    x }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mice}\NormalTok{(}\AttributeTok{m =} \DecValTok{5}\NormalTok{, }
               \AttributeTok{maxit =} \DecValTok{1}\NormalTok{,}
               \AttributeTok{method =} \StringTok{"cart"}\NormalTok{,}
               \AttributeTok{minbucket =} \DecValTok{3}\NormalTok{,}
               \AttributeTok{cp =} \FloatTok{1e{-}08}\NormalTok{,}
               \AttributeTok{predictorMatrix =}\NormalTok{ pred,}
               \AttributeTok{post =}\NormalTok{ post,}
               \AttributeTok{where =} \FunctionTok{matrix}\NormalTok{(}\ConstantTok{TRUE}\NormalTok{, }\FunctionTok{nrow}\NormalTok{(data), }\FunctionTok{ncol}\NormalTok{(data)),}
               \AttributeTok{print =}\NormalTok{ F)}
\NormalTok{\}, }\AttributeTok{.options =} \FunctionTok{furrr\_options}\NormalTok{(}\AttributeTok{seed =} \FunctionTok{as.integer}\NormalTok{(}\DecValTok{123}\NormalTok{)))}
\end{Highlighting}
\end{Shaded}
